### 2020-07-03 chapters/introduction.tex
Capitalization
Document Structure section

\section{Document structure}

\textcolor{red}{TODO at the end rewrite and relink this}

This section merely sums up how each of the following Chapters contributes to this Thesis.

%In Chapter \ref{chap:background} of this document we brief the reader with the necessary background and relevant concepts needed to understand the following Chapters.

%In Chapter \ref{chap:sota} we examine the state of the art in the area, analyzing the most recent work done and classifying it into subgroups.

%In Chapter \ref{chap:approach} we define the scope of this project, the research questions we intend to answer, our experimental methodology and our future planning.

%In Chapter \ref{chap:conclusion} we summarize our contributions.

>>>>

\section{Document Structure}

This section merely sums up how each of the following chapters contributes to this thesis.

In Chapter \ref{chap:background} of this document, we brief the reader with the necessary background and relevant concepts needed to understand the following work, namely the topics of Large Scale Data Processing, Sliding Window Aggregations and Outlier Detection, as well as all the sub-topics inherent to them.

In Chapter \ref{chap:sota}, we examine state of the art methods related with the previously mentioned topics and discuss shortcomings, strengths and the applicability of such methods to our hypothesis.

In Chapter \ref{chap:statement}, we define the problem this thesis aims to solve, the issues with state of the art solutions, our proposed solution, the assumptions made on it and the research questions we intend to answer.

In Chapter \ref{chap:my-work}, we discuss initial thought solutions and reasons to discard them before presenting our distribution monitoring method.

In Chapter \ref{chap:validation}, we describe the set of experiments made and the datasets used. We start with single feature experiments on synthetic data, then multi feature analysis and finally move on to multi feature analysis on real data.

In Chapter \ref{chap:conclusion}, we draw our final conclusions. We reiterate our hypothesis and research questions and we provide answers to them. We summarize our contributions and make explicit current issues to be addressed as future work.
